Reviving the Lost Art of Combinator Graph Reduction

### 2022-12-18 experiments/superg/doc/paper/paper.tex
Note on folding ctx merge into semantic.

\begin{equation*}
    \begin{array}{l l l l}
        \lazyeta & z         & = & \emptyset \models V                                                          \\
        \lazyeta & s \ e     & = & \Gamma,f \models c                                                           \\
                 &           &   & \text{where } (\Gamma \models c) := \lazyeta e                               \\
        \\
        \lazyeta & \lambda e & = & \emptyset \models I                                                          \\
                 &           &   & \text{where } (\emptyset \models V) := \lazyeta e                            \\
        \lazyeta & \lambda e & = & \emptyset \models K \; c                                                     \\
                 &           &   & \text{where } (\emptyset \models c) := \lazyeta e                            \\
        \lazyeta & \lambda e & = & (\emptyset \models K) \coprod_\eta (\Gamma \models c)                        \\
                 &           &   & \text{where } (\Gamma,f \models c) := \lazyeta e                             \\
        \lazyeta & \lambda e & = & \Gamma \models K \; c                                                        \\
                 &           &   & \text{where } (\Gamma,t \models c) := \lazyeta e                             \\
        \\
        \lazyeta & e_1 \ e_2 & = & (\Gamma \models ((\Gamma_1 \models c_1) \coprod_\eta (\Gamma_2 \models c_2)) \\
                 &           &   & \text{where } (\Gamma_1 \models c_1) := \lazyeta e_1                         \\
                 &           &   & \text{where } (\Gamma_2 \models c_2) := \lazyeta e_2                         \\
                 &           &   & \text{where } \Gamma := \Gamma_1 \sqcup \Gamma_2                             \\
    \end{array}
\end{equation*}

\textbf{TODO: } Check this, possibly need to take (C d, V) = N (C d)
The context merge function $\sqcup$ is unchanged, but we do have some new cases for the semantic function:

@@

>>>>

\begin{equation*}
    \begin{array}{l l l l}
        \lazyeta & z         & = & \emptyset \models V                                                          \\
        \lazyeta & s \ e     & = & \Gamma,f \models c                                                           \\
                 &           &   & \text{where } (\Gamma \models c) := \lazyeta e                               \\
        \\
        \lazyeta & \lambda e & = & \emptyset \models I                                                          \\
                 &           &   & \text{where } (\emptyset \models V) := \lazyeta e                            \\
        \lazyeta & \lambda e & = & \emptyset \models K \; c                                                     \\
                 &           &   & \text{where } (\emptyset \models c) := \lazyeta e                            \\
        \lazyeta & \lambda e & = & (\emptyset \models K) \coprod_\eta (\Gamma \models c)                        \\
                 &           &   & \text{where } (\Gamma,f \models c) := \lazyeta e                             \\
        \lazyeta & \lambda e & = & \Gamma \models K \; c                                                        \\
                 &           &   & \text{where } (\Gamma,t \models c) := \lazyeta e                             \\
        \\
        \lazyeta & e_1 \ e_2 & = & (\Gamma \models ((\Gamma_1 \models c_1) \coprod_\eta (\Gamma_2 \models c_2)) \\
                 &           &   & \text{where } (\Gamma_1 \models c_1) := \lazyeta e_1                         \\
                 &           &   & \text{where } (\Gamma_2 \models c_2) := \lazyeta e_2                         \\
                 &           &   & \text{where } \Gamma := \Gamma_1 \sqcup_\eta \Gamma_2                        \\
    \end{array}
\end{equation*}

Our context merge function $\sqcup$ now also depends on the compiled expression, since we have a special case for $V$:

\begin{equation*}
    \begin{array}{l l l l l}
        (\Gamma_1,\_ \models c_1) & \sqcup_\eta & (\emptyset \models V)     & = & \Gamma_1,t                        \\
        (\emptyset \models V)     & \sqcup_\eta & (\Gamma_2,\_ \models c_2) & = & \Gamma_2,t                        \\
        (\emptyset \models c_1)   & \sqcup_\eta & (\emptyset \models V)     & = & t                                 \\
        (\emptyset \models V)     & \sqcup_\eta & (\emptyset \models c_2)   & = & t                                 \\
        (\emptyset \models V)     & \sqcup_\eta & (\emptyset \models V)     & = & \mathbf{impossible}               \\
        \\
        % Original ones
        (\Gamma_1 \models c_1)    & \sqcup_\eta & (\emptyset \models c_2)   & = & \Gamma_1                          \\
        (\emptyset \models c_1)   & \sqcup_\eta & (\Gamma_2 \models c_2)    & = & \Gamma_2                          \\
        (\Gamma_1,t \models c_1)  & \sqcup_\eta & (\Gamma_2,\_ \models c_2) & = & (\Gamma_1 \sqcup_\eta \Gamma_2),t \\
        (\Gamma_1,\_ \models c_1) & \sqcup_\eta & (\Gamma_2,t \models c_2)  & = & (\Gamma_1 \sqcup_\eta \Gamma_2),t \\
        (\Gamma_1,f \models c_1)  & \sqcup_\eta & (\Gamma_2,f \models c_2)  & = & (\Gamma_1 \sqcup_\eta \Gamma_2),f \\
    \end{array}
\end{equation*}

The $V$ value effectively encodes an additional implicit used element in the context.
We also have some new cases for the semantic function:

@@

With the addition of the expression value to $\sqcup_\eta$, the function now takes the same input as $\coprod_\eta$ and has very similar matching patterns.
Our implementation, therefore, folds context merging into $\coprod_\eta$ to make the code more concise.
